Designing Efficient Smart Camera Networks For Public Saftey

### 2013-10-16 Paper/main.tex
starting taxonomy

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Removing Physical Limits, \textsc{Secuirity cameras of the Future}}

% author names and affiliations
% transmag papers use the long conference author name format.

@@

% for Transactions on Magnetics papers, we must declare the abstract and
% index terms PRIOR to the title within the \IEEEtitleabstractindextext
% IEEEtran command as these need to go into the title area created by
% \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, magnetics, paper, template.
\end{IEEEkeywords}}

% make the title area
\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

@@

% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} paper discusses ...

@@

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

@@

\section{Requirements for today's wireless Smart Camera Networks}
\-- What are some more recent technologies being used and discovered by
researchers today. \\

@@

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsection{Software}
\subsubsection{Image Processing}
\- Considering the constraints of the system in terms of price and hardware, it is used techniques of background subtraction to do the object detection. When started, the program keep taking pictures and process them using Mixture of Gaussian (MoG) method by Stauffer and Grimson. With the foreground in hands we find the contours and then a bounded box is applied following the contours' limit. To remove some noise and false detection a step is added to ignore objects of small size. The object classification is the most processor consumption  processes for most of the pedestrian detection systems, because it is used training techniques to classify the objects based on a previous stored database. In our case, to reduce the process we classify the objects by looking at their dimensions, they are classified as human if the height is two times bigger than the width we classify as a person. \\
\begin{figure}[h!]
\centering
\includegraphics[scale=0.3]{imageprocessing}
\end{figure}	
\- This light system can generate some false alarms, but in association with the whole system, and its sensors, it can be improved for a better performance. There are other more robust object detection methods that could be used, but we would have a very low fps rate. \\
\- We developed using the Raspberry Pi camera module, which has already an API in C language and capable of capturing 1920x1080 resolution color images with 30 fps rate. For the image processing, we chose the Open Source Computer Vision Library (OpenCv). Our computer vision system is developed in C++ for better integration between the OpenCV and the API.\\

@@

\section{Conclusion}
\-- tie up paper

% use section* for acknowledgement
\section*{Acknowledgment}

\-- might not need this ...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Kevin Abas}
Biography text here.
\end{IEEEbiographynophoto}

@@

@@

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

>>>>

% ** BIBTEXT PACKAGE **
\usepackage{cite}

%%----------------------------------------------------------------------

\begin{document}

%% ***********************  THE TITLE **********************************

\title{Designing Efficient Smart Camera Networks For Public Saftey}

%% ***********************  AUTHORS ************************************

@@

%% ***********************  AUTHORS ************************************

\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}

%% ********************** IEEE KEYWORDS ********************************

\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, magnetics, paper, template.
\end{IEEEkeywords}}

%% Title Configurations (From Template)
\maketitle
\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

%% *********************  BEGIN PAPER **********************************

@@

\IEEEPARstart{T}{his} paper discusses ...

@@

@@

%%Requirements for today's wireless Smart Camera Networks
\section{Smart Camera Surveillance}
Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes in public spaces. To
understand how these state of the art systems are improving on designs of the past one must define what makes these surveillance systems "smart". These
smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network resource
utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment scenarios. Then in
almost every application considering power consumption of each node is very important if one is give an analysis of the systems efficiency. If these
systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring that the data recorded
is actually quality information that could be used by officials. \\

@@

\subsection{Software}
\subsubsection{Image Processing}
\- Considering the constraints of the system in terms of price and hardware, it is used techniques of background subtraction to do the object detection. When started, the program keep taking pictures and process them using Mixture of Gaussian (MoG) method by Stauffer and Grimson. With the foreground in hands we find the contours and then a bounded box is applied following the contours' limit. To remove some noise and false detection a step is added to ignore objects of small size. The object classification is the most processor consumption  processes for most of the pedestrian detection systems, because it is used training techniques to classify the objects based on a previous stored database. In our case, to reduce the process we classify the objects by looking at their dimensions, they are classified as human if the height is two times bigger than the width we classify as a person. \\
\begin{figure}[h!]
\centering
\includegraphics[scale=0.3]{imageprocessing.jpg}
\end{figure}	
\- This light system can generate some false alarms, but in association with the whole system, and its sensors, it can be improved for a better performance. There are other more robust object detection methods that could be used, but we would have a very low fps rate. \\
\- We developed using the Raspberry Pi camera module, which has already an API in C language and capable of capturing 1920x1080 resolution color images with 30 fps rate. For the image processing, we chose the Open Source Computer Vision Library (OpenCv). Our computer vision system is developed in C++ for better integration between the OpenCV and the API.\\

@@

\section{Conclusion}
\-- tie up paper
~\cite{DSPcam}
~\cite{HuSIMS}
~\cite{Citric}
~\cite{OmniEye}
~\cite{ScoutNode}
~\cite{SensEye}
~\cite{WiFLIP}

%% *************************  END PAPER **********************************

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
%\ifCLASSOPTIONcaptionsoff
%  \newpage
%\fi

%% ******************  REFERENCE SECTION **********************************

\bibliography{Bib.bib}{}
\bibliographystyle{plain}

%% ******************  AUTHOR BIOGRAPHIES *********************************

\begin{IEEEbiographynophoto}{Kevin Abas}
Biography text here.
\end{IEEEbiographynophoto}

@@

%%------------------------------------------------------------------------

@@
